---
# IMPORTANT: Change settings here, but DO NOT change the spacing.
# Remove comments and add values where applicable.
# The descriptions below should be self-explanatory

title: "Financial Econometrics 871 Practical Exam 2022: Question 2"
subtitle: "Question 2"

documentclass: "elsarticle"

# --------- Thesis title (Optional - set to FALSE by default).
# You can move the details below around as you please.
Thesis_FP: FALSE
# Entry1: "An unbelievable study with a title spanning multiple lines."
# Entry2: "\\textbf{Nico Katzke}" # textbf for bold
# Entry3: "A thesis submitted toward the degree of Doctor of Philosophy"
# Uni_Logo: Tex/Logo.png # Place a logo in the indicated location (from your root, e.g. defaults to ~/Tex/Logo.png) and uncomment this line. Leave uncommented for no image
# Logo_width: 0.3 # If using a logo - use this to set width (size) of image
# Entry4: "Under the supervision of: \\vfill Prof. Joe Smith and Dr. Frank Smith"
# Entry5: "Stellenbosch University"
# Entry6: April 2020
# Entry7:
# Entry8:

# --------- Front Page
# Comment: ----- Follow this pattern for up to 5 authors
AddTitle: TRUE # Use FALSE when submitting to peer reviewed platform. This will remove author names.
Author1: "Tian Cater"  # First Author - note the thanks message displayed as an italic footnote of first page.
Ref1: "University of Stellenbosch, Western Cape, South Africa^[2022-11-27]" # First Author's Affiliation
Email1: "19025831\\@sun.ac.za" # First Author's Email address

#Author2: "John Smith"
#Ref2: "Some other Institution, Cape Town, South Africa"
#Email2: "John\\@gmail.com"
#CommonAffiliation_12: TRUE # If Author 1 and 2 have a common affiliation. Works with _13, _23, etc.

#Author3: "John Doe"
#Email3: "Joe\\@gmail.com"

#CorrespAuthor_1: TRUE  # If corresponding author is author 3, e.g., use CorrespAuthor_3: TRUE

# Comment out below to remove both. JEL Codes only given if keywords also given.
#keywords: "Multivariate GARCH \\sep Kalman Filter \\sep Copula" # Use \\sep to separate
#JELCodes: "L250 \\sep L100"

# ----- Manage headers and footers:
#BottomLFooter: $Title$
#BottomCFooter:
#TopLHeader: \leftmark # Adds section name at topleft. Remove comment to add it.
BottomRFooter: "\\footnotesize Page \\thepage" # Add a '#' before this line to remove footer.
addtoprule: TRUE
addfootrule: TRUE               # Use if footers added. Add '#' to remove line.

# --------- page margins:
margin: 2.3 # Sides
bottom: 2 # bottom
top: 2.5 # Top
HardSet_layout: TRUE # Hard-set the spacing of words in your document. This will stop LaTeX squashing text to fit on pages, e.g.
# This is done by hard-setting the spacing dimensions. Set to FALSE if you want LaTeX to optimize this for your paper.

# --------- Line numbers
linenumbers: FALSE # Used when submitting to journal

# ---------- References settings:
# You can download cls format here: https://www.zotero.org/ - simply search for your institution. You can also edit and save cls formats here: https://editor.citationstyles.org/about/
# Hit download, store it in Tex/ folder, and change reference below - easy.
bibliography: Tex/ref.bib       # Do not edit: Keep this naming convention and location.
csl: Tex/harvard-stellenbosch-university.csl # referencing format used.
# By default, the bibliography only displays the cited references. If you want to change this, you can comment out one of the following:
#nocite: '@*' # Add all items in bibliography, whether cited or not
# nocite: |  # add specific references that aren't cited
#  @grinold2000
#  @Someoneelse2010

# ---------- General:
RemovePreprintSubmittedTo: TRUE  # Removes the 'preprint submitted to...' at bottom of titlepage
Journal: "Journal of Finance"   # Journal that the paper will be submitting to, if RemovePreprintSubmittedTo is set to TRUE.
toc: FALSE                       # Add a table of contents
numbersections: TRUE             # Should sections (and thus figures and tables) be numbered?
fontsize: 11pt                  # Set fontsize
linestretch: 1.2                # Set distance between lines.
link-citations: TRUE            # This creates dynamic links to the papers in reference list.

### Adding additional latex packages:
# header-includes:
#    - \usepackage{colortbl} # Add additional packages here.

output:
  pdf_document:
    keep_tex: TRUE
    template: Tex/TexDefault.txt
    fig_width: 3.5 # Adjust default figure sizes. This can also be done in the chunks of the text.
    fig_height: 3.5
abstract: |
  Economists recently pointed out that the current yield spreads in SA mid to longer-dated bond yields have since 2020 been the highest in decades. I analyse the current yield spreads in the local bond market for this question. In addition, I compare the local spread to comparable international spreads, observe the correlation between the local bond spreads and the USD-ZAR level, and consider the SA 10 Year Break-Even inflation estimate. The findings suggest that the current yield spreads in SA mid to longer-dated bond yields have been the highest in decades since 2020 and even 2018. Additionally, the strong co-movement between the SA bond yield spread and the ZAR/USD exchange rate has remained strong; however, it marginally diminished between 2010 and 2016. Lastly, the SA average inflation rate has not surpassed the BE inflation yield estimate since 2014, indicating that fixed investment has been firmly preferred over index-linked bond investment. 

---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

# Lets load in example data, and see how this can be stored and later called from your 'data' folder.
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)

pacman::p_load("RiskPortfolios", "FactoMineR", "factoextra", "broom")
pacman::p_load("tidyverse","fmxdat", "dplyr", "rmsfuns", "PerformanceAnalytics", "tbl2xts", "xts", "rportfolios", "Texevier", "kableExtra", "ggplot2", "extrafont", "devtools")


SA_bonds <- read_rds("C:/Users/tianc/Rproj/FinMetrics871_Exam/19025831/data/SA_Bonds.rds")
BE_Infl <- read_rds("C:/Users/tianc/Rproj/FinMetrics871_Exam/19025831/data/BE_Infl.rds")
bonds_2y <- read_rds("C:/Users/tianc/Rproj/FinMetrics871_Exam/19025831/data/bonds_2y.rds")
bonds_10y <- read_rds("C:/Users/tianc/Rproj/FinMetrics871_Exam/19025831/data/bonds_10y.rds")
usdzar <- read_rds("C:/Users/tianc/Rproj/FinMetrics871_Exam/19025831/data/usdzar.rds")
ZA_Infl <- read_rds("C:/Users/tianc/Rproj/FinMetrics871_Exam/19025831/data/ZA_Infl.rds")
IV <- read_rds("C:/Users/tianc/Rproj/FinMetrics871_Exam/19025831/data/IV.rds")


Countries_to_compare <- c("Germany", "ZA", "US", "CHINA", "Japan", "Brazil")

bonds_10y_adj <- bonds_10y |> pivot_wider(names_from = "Name", values_from = "Bond_10Yr") |> 
    
    left_join(SA_bonds |> select(c(date, ZA_10Yr)), by="date") |> 
    
    pivot_longer(cols = -date, names_to = "Name", values_to = "Bond_10Yr")|> 
    
    mutate(Name = gsub("_10Yr", "", Name)) |> 
    
    filter((Name %in% Countries_to_compare))  # Only filter the desired countries

# Upon initial attempt to format bonds_2y, I realised there is a duplicate entry, identified by the following 

duplicate_entries_identification <- bonds_2y %>%
                                    dplyr::group_by(date, Name) %>%
                                    dplyr::summarise(n = dplyr::n(), .groups = "drop") %>%
                                    dplyr::filter(n > 1L)

# Since the duplicate entry is "Chile_2yr", I remove Chile in order to pivot_wider. 

bonds_2y_adj <- bonds_2y |> filter(!(Name %in% c("Chile_2yr"))) |>  # remove chile
    
    pivot_wider(names_from = "Name", values_from = "Bond_2Yr") |> 
    
    left_join(SA_bonds |> select(c(date, ZA_2Yr)), by="date") |> 
    
    pivot_longer(cols = -date, names_to = "Name", values_to = "Bond_2Yr") |> 
    
    mutate(Name = gsub("_2yr", "", Name)) |> mutate(Name = gsub("_2Yr", "", Name)) |> 
    
    filter(Name %in% Countries_to_compare) 

# Now I proceed to merge the 2Yr and 10Yr global yields and their spreads in one tbl

Global_bonds_data <- inner_join(bonds_2y_adj, bonds_10y_adj, by= c("date", "Name")) |> 
    
    mutate(Spread = Bond_10Yr - Bond_2Yr)

# Partition ZA and US yield spread data into post and pre GFC and convert to xts

pre_GFC_xts <- Global_bonds_data|> filter(Name %in% c("ZA", "US")) |> select(date, Name, Spread) |> 
     
    filter(date <= lubridate::ymd(20081031)) |>  
    
    filter(date >= lubridate::ymd(19991206)) |>  # Start from ZA's first observation
    
    tbl_xts(cols_to_xts = Spread, spread_by = Name) 
    
post_GFC_xts <- Global_bonds_data|> filter(Name %in% c("ZA", "US")) |> select(date,Name ,Spread) |> 
     
    filter(date >= lubridate::ymd(20081031)) |> tbl_xts(cols_to_xts = Spread, spread_by = Name) 

# Use performance analytics package for statistical table

table_pre_GFC <- PerformanceAnalytics::table.Stats(pre_GFC_xts, ci=0.95, digits = 2)

table_post_GFC <- PerformanceAnalytics::table.Stats(post_GFC_xts, ci=0.95, digits = 2)

# Only select the desired stats

table_pre_GFC <- table_pre_GFC[c(3,6,9,10,11,12,14,15,16),] 
table_post_GFC <- table_post_GFC[c(3,6,9,10,11,12,14,15,16),] 

# Break-even inflation is the difference between the nominal yield on a fixed-rate investment and the real yield (fixed spread) on an inflation-linked investment of similar maturity and credit quality. If inflation averages more than the break-even, the inflation-linked investment will outperform the fixed-rate.

# Find the monthly values of BE Infl Yiels to compare to monthly inflation data 

BE_Infl_adj <- BE_Infl |> mutate(YearMonth = format(date, "%Y-%m")) |> 
    
    group_by(YearMonth) |> filter(date == last(date)) |> 
    
    ungroup() |> rename(BEI = Price)|> select(YearMonth, BEI)

# Notice that the number of days withing the BE inflation set is incorrect, so I rather use YearMonth as common column, 
# And then utilise the dateconverter command. 


```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

# Comparing Global Bond Market Yield Spreads 

Figure \ref{Figure1} shows the bond market yield spreads for SA, the US, Brazil, Germany, China, and Japan, respectively. Visually, \ref{Figure1} confirms the notion that the current yield spreads in local mid to longer-dated bond yields have since 2020 been the highest in decades.  The SA Bond yield spread has been significantly more volatile than those of Germany, China, the US, and Japan while having less volatility in the last few years than Brazil.
```{r Global_bonds_plot,  warning =  FALSE, fig.align = 'center', fig.cap = "Global Bond Market Yield Spreads \\label{Figure1}", fig.ext = 'png', fig.height = 4, fig.width = 6}

Global_bonds_plot <-    Global_bonds_data |> select(date,Name ,Spread) |> 
    
    ggplot() + 
  
  geom_line(aes(date, Spread , color = Name), size = 0.8, alpha = 0.7) +
  
   fmxdat::theme_fmx(title.size = fmxdat::ggpts(30), 
                    subtitle.size = fmxdat::ggpts(0),
                    caption.size = fmxdat::ggpts(25),
                    CustomCaption = T) + 
    
  fmxdat::fmx_cols() + 
  
  labs(x = "", y = "Yield Spread (%)", caption = "Note:\nCalculation own",
       title = "Global Bond Market Yield Spreads",
       subtitle = "")
  
# Finplot for finishing touches:

fmxdat::finplot(Global_bonds_plot, x.vert = T, x.date.type = "%Y", x.date.dist = "2 years", darkcol = F)


```

In considering the SA and US bond yield spreads against the ZAR/USD exchange rate, graphed in \ref{Figure2} below, it is evident that the co-movements between the ZAR/USD and the SA bonds yield spread have over time been relatively strong, however, between the periods of 2010 and 2016 this positive correlation has diminished, likely due to the large open market asset purchases by the FED that distorts the international spillovers.
```{r SA_Bonds_Plot,  warning =  FALSE, fig.align = 'center', fig.cap = "SA Bond Yields, Spread, and ZAR/USD Exchange Rate \\label{Figure2}", fig.ext = 'png', fig.height = 3.5, fig.width = 6}

SA_Bonds_Plot <- Global_bonds_data |> filter(Name %in% c("ZA")) |> left_join(usdzar |> select(-Name), by = "date") |> 
    
    rename( R_USD = Price) |> pivot_longer(cols = -c(date, Name), names_to = "Description", values_to = "Values") |> 
    
    ggplot() + 
  
  geom_line(aes(date, Values , color = Description), size = 0.8, alpha = 0.7) +
  
   fmxdat::theme_fmx(title.size = fmxdat::ggpts(30), 
                    subtitle.size = fmxdat::ggpts(0),
                    caption.size = fmxdat::ggpts(25),
                    CustomCaption = T) + 
    
  fmxdat::fmx_cols() + 
  
  labs(x = "", y = "", caption = "Note:\nCalculation own",
       title = "SA Bond Yields, Spread, and R/USD Exchange Rate",
       subtitle = "")
    
# Finplot for finishing touches:

fmxdat::finplot(SA_Bonds_Plot, x.vert = T, x.date.type = "%Y", x.date.dist = "2 years", darkcol = F)


```

To provide an additional perspective, the statistics in Table \ref{Table1} compared the SA and US bond yield spread before and after the Global Financial Crises (GFC). Overall, considering the SA and US separately and somewhat loosely, as done here, the volatility in the SA bond yield has remained relatively similar compared to its pre- and post-GFC.

```{r stats table, results='asis', fig.cap= " SA vs US Bond Yields Statistics: Pre GFC vs Post GFC. \\label{Figure3}"}

final_stats_table <- 
    
    table_pre_GFC |>  data.frame() |>  tibble::rownames_to_column()|> 
    left_join(table_post_GFC|>  data.frame() |>  tibble::rownames_to_column(), by = "rowname" ) |> 
    rename(Description = rowname) |> 
    
    knitr::kable(col.names = c("Description",
                           "SA",
                           "US",
                           "SA", "US"), caption = "SA vs US Bond Yield Spread Statistics: Pre GFC vs Post GFC. \\label{Table1}", booktabs = T) |> kable_classic(full_width = F) |> 
    
    add_header_above(c(" " = 1, "Pre GFC" = 2, "Post GFC" = 2))



final_stats_table


```

# SA Break-Even Inflation 

Lastly, I analyse the SA Break-Even inflation yield estimate and compare it to the SA inflation rate (Figure \ref{Figure4}). Break-even inflation is the difference between the nominal yield on a fixed-rate investment and the real yield (fixed spread) on an inflation-linked investment of similar maturity and credit quality. If inflation averages more than the break-even, the inflation-linked investment will outperform the fixed rate.

From Figure \ref{Figure4}, the SA average inflation rate has not surpassed the BE inflation yield estimate since 2014, indicating that fixed investment has been firmly preferred over index-linked bond investment.


```{r BEI_infl_plot,  warning =  FALSE, fig.align = 'center', fig.cap = "SA Break-Even Inflation Yield Versus Average Inflation Rate \\label{Figure4}", fig.ext = 'png', fig.height = 3.5, fig.width = 6}


BEI_infl_plot <- ZA_Infl |> mutate(YearMonth = format(date, "%Y-%m") ) |> 
    
    select(YearMonth, Price) |> rename(Inflation = Price) |> 
    
    right_join(BE_Infl_adj, by = "YearMonth") |> 
    
    mutate(date = dateconverter(as.Date("2012-05-01"), as.Date("2021-10-29"), "calendarEOM")) |> 
    
    select(-YearMonth) |> 
    
    pivot_longer(cols = -date, names_to = "Name", values_to = "Values") |> 
    
     ggplot() + 
  
  geom_line(aes(date, Values , color = Name), size = 0.8, alpha = 0.7) +
  
   fmxdat::theme_fmx(title.size = fmxdat::ggpts(30), 
                    subtitle.size = fmxdat::ggpts(0),
                    caption.size = fmxdat::ggpts(25),
                    CustomCaption = T) + 
    
  fmxdat::fmx_cols() + 
  
  labs(x = "", y = "%", caption = "Note:\nCalculation own",
       title = "SA Break-Even Inflation Yield Versus Average Inflation Rate",
       subtitle = "")

# Finplot for finishing touches:

fmxdat::finplot(BEI_infl_plot, x.vert = T, x.date.type = "%Y", x.date.dist = "2 years", darkcol = F)


```




<!-- Make title of bibliography here: -->
<!-- \newpage -->

\newpage

# References {-}

<div id="refs"></div>
