---
# IMPORTANT: Change settings here, but DO NOT change the spacing.
# Remove comments and add values where applicable.
# The descriptions below should be self-explanatory

title: "Financial Econometrics 871 Practical Exam 2022: Question 3"
subtitle: "Question 3"

documentclass: "elsarticle"

# --------- Thesis title (Optional - set to FALSE by default).
# You can move the details below around as you please.
Thesis_FP: FALSE
# Entry1: "An unbelievable study with a title spanning multiple lines."
# Entry2: "\\textbf{Nico Katzke}" # textbf for bold
# Entry3: "A thesis submitted toward the degree of Doctor of Philosophy"
# Uni_Logo: Tex/Logo.png # Place a logo in the indicated location (from your root, e.g. defaults to ~/Tex/Logo.png) and uncomment this line. Leave uncommented for no image
# Logo_width: 0.3 # If using a logo - use this to set width (size) of image
# Entry4: "Under the supervision of: \\vfill Prof. Joe Smith and Dr. Frank Smith"
# Entry5: "Stellenbosch University"
# Entry6: April 2020
# Entry7:
# Entry8:

# --------- Front Page
# Comment: ----- Follow this pattern for up to 5 authors
AddTitle: TRUE # Use FALSE when submitting to peer reviewed platform. This will remove author names.
Author1: "Tian Cater"  # First Author - note the thanks message displayed as an italic footnote of first page.
Ref1: "University of Stellenbosch, Western Cape, South Africa^[2022-11-27]" # First Author's Affiliation
Email1: "19025831\\@sun.ac.za" # First Author's Email address

#Author2: "John Smith"
#Ref2: "Some other Institution, Cape Town, South Africa"
#Email2: "John\\@gmail.com"
#CommonAffiliation_12: TRUE # If Author 1 and 2 have a common affiliation. Works with _13, _23, etc.

#Author3: "John Doe"
#Email3: "Joe\\@gmail.com"

#CorrespAuthor_1: TRUE  # If corresponding author is author 3, e.g., use CorrespAuthor_3: TRUE

# Comment out below to remove both. JEL Codes only given if keywords also given.
#keywords: "Multivariate GARCH \\sep Kalman Filter \\sep Copula" # Use \\sep to separate
#JELCodes: "L250 \\sep L100"

# ----- Manage headers and footers:
#BottomLFooter: $Title$
#BottomCFooter:
#TopLHeader: \leftmark # Adds section name at topleft. Remove comment to add it.
BottomRFooter: "\\footnotesize Page \\thepage" # Add a '#' before this line to remove footer.
addtoprule: TRUE
addfootrule: TRUE               # Use if footers added. Add '#' to remove line.

# --------- page margins:
margin: 2.3 # Sides
bottom: 2 # bottom
top: 2.5 # Top
HardSet_layout: TRUE # Hard-set the spacing of words in your document. This will stop LaTeX squashing text to fit on pages, e.g.
# This is done by hard-setting the spacing dimensions. Set to FALSE if you want LaTeX to optimize this for your paper.

# --------- Line numbers
linenumbers: FALSE # Used when submitting to journal

# ---------- References settings:
# You can download cls format here: https://www.zotero.org/ - simply search for your institution. You can also edit and save cls formats here: https://editor.citationstyles.org/about/
# Hit download, store it in Tex/ folder, and change reference below - easy.
bibliography: Tex/ref.bib       # Do not edit: Keep this naming convention and location.
csl: Tex/harvard-stellenbosch-university.csl # referencing format used.
# By default, the bibliography only displays the cited references. If you want to change this, you can comment out one of the following:
#nocite: '@*' # Add all items in bibliography, whether cited or not
# nocite: |  # add specific references that aren't cited
#  @grinold2000
#  @Someoneelse2010

# ---------- General:
RemovePreprintSubmittedTo: TRUE  # Removes the 'preprint submitted to...' at bottom of titlepage
Journal: "Journal of Finance"   # Journal that the paper will be submitting to, if RemovePreprintSubmittedTo is set to TRUE.
toc: FALSE                       # Add a table of contents
numbersections: TRUE             # Should sections (and thus figures and tables) be numbered?
fontsize: 11pt                  # Set fontsize
linestretch: 1.2                # Set distance between lines.
link-citations: TRUE            # This creates dynamic links to the papers in reference list.

### Adding additional latex packages:
# header-includes:
#    - \usepackage{colortbl} # Add additional packages here.

output:
  pdf_document:
    keep_tex: TRUE
    template: Tex/TexDefault.txt
    fig_width: 3.5 # Adjust default figure sizes. This can also be done in the chunks of the text.
    fig_height: 3.5
abstract: |
  To answer this question, I use the information on the ALSI (J200) and SWIX (J400) top 40 Indexes and compare the SWIX and ALSI methodologies by looking at the performance of different sector exposures and stock concentrations over time. The findings show that the (uncapped) ALSI has performed relatively better since the onset of COVID-19 than the SWIX and can be attributed to a higher weight assigned to the better-performing Resources sector. In addition, through analysing the impact that 6% and 10% capping levels would have had on both the SWIX and ALSI, it is apparent that a 6% cap on the ALSI would have significantly reduced its performance in the past few years due to slicing the weights on the higher returning Resources sector. On the other hand, the 10% cap on SWIX would have improved its return since the onset of COVID, likely due to a reduction in weighted contribution from the weaker-performing Industrial and Financial sectors.
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

# Lets load in example data, and see how this can be stored and later called from your 'data' folder.
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)

pacman::p_load("RiskPortfolios", "FactoMineR", "factoextra", "broom")
pacman::p_load("tidyverse","fmxdat", "dplyr", "rmsfuns", "PerformanceAnalytics", "tbl2xts", "xts", "rportfolios", "Texevier", "kableExtra", "ggplot2", "extrafont", "devtools")

T40 <- read_rds("C:/Users/tianc/Rproj/FinMetrics871_Exam/19025831/data/T40.rds") # There are 92 stocks in this tbl

RebDays <- read_rds("C:/Users/tianc/Rproj/FinMetrics871_Exam/19025831/data/Rebalance_days.rds")

Capped_SWIX <- read_rds("C:/Users/tianc/Rproj/FinMetrics871_Exam/19025831/data/Capped_SWIX.rds") # This is the Monthly Capped and Weighted Portf Returns for SWIX Index (J433)

# I first shrink the dataframe to include only what in needed

T40_a <- T40 |> select(-Short.Name) |> 
    
    mutate(Tickers = gsub(" SJ Equity", "", Tickers))  # Remove clutter in Tickers names


# I generate a tbl calculating both Indexes weighted returns by hand

df_Port_ret <- T40_a |> 
    
    mutate(J400 = coalesce(J400, 0)) |> 
    
    mutate(J400 = coalesce(J400, 0)) |> 
    
    mutate(ALSI_wret = Return*J200) |> 
    
    mutate(SWIX_wret = Return*J400) |> 
    
    arrange(date) |> 
    
    group_by(date) |> 
    
    mutate(ALSI_pret = sum(ALSI_wret)) |> 
    
    mutate(SWIX_pret = sum(SWIX_wret)) 

# Lets calculate the weighted portfolio daily return for ALSI and SWIX using Safe_Returns to verify my by hand calculation

Wghts_ALSI_xts <- T40_a |> select(date, Tickers , J200) |> tbl_xts(cols_to_xts = J200, spread_by = Tickers)

Wghts_SWIX_xts <- T40_a |> select(date, Tickers , J400) |> tbl_xts(cols_to_xts = J400, spread_by = Tickers)

Returns_xts <- T40_a |> select(date, Tickers , Return) |> tbl_xts(cols_to_xts = Return, spread_by = Tickers)

# Set NA's to null to use PA's Safe_returns.Portfolio command

Wghts_ALSI_xts[is.na(Wghts_ALSI_xts)] <- 0
Wghts_SWIX_xts[is.na(Wghts_SWIX_xts)] <- 0
Returns_xts[is.na(Returns_xts)] <- 0

# Now I calculate the weighed (uncapped) portfolio returns

Port_Ret_ALSI <- rmsfuns::Safe_Return.portfolio(R = Returns_xts, weights = Wghts_ALSI_xts, lag_weights = T) |> 
    
                 xts_tbl() |> rename(ALSI_Ret = portfolio.returns)

Port_Ret_SWIX <- rmsfuns::Safe_Return.portfolio(R = Returns_xts, weights = Wghts_SWIX_xts, lag_weights = T) |> 
    
                 xts_tbl() |> rename(SWIX_Ret = portfolio.returns)

# Now I combine the above two weighted portfolio returns

Merged_Port_Ret <- inner_join(Port_Ret_ALSI, Port_Ret_SWIX, by= "date")

# I verify that my by hand calc and the Safe_return calc is the same:
# df_Port_ret |> select(date, ALSI_pret, SWIX_pret) |> group_by(date, ALSI_pret, SWIX_pret ) |> summarise()
# Happy ---> They are the same

# Now I proceed to calculate the Portfolios' cumulative return and plot it

Cum_ret <- Merged_Port_Ret |> arrange(date) |> 
    
    mutate(across(.cols = -date, .fns = ~cumprod(1 + .))) |> 
    
    mutate(across(.cols = -date, .fns = ~./first(.))) |> # Start at 1
    
    rename(ALSI = ALSI_Ret, SWIX= SWIX_Ret) |> 
    
    pivot_longer(cols=-date, names_to = "Index", values_to = "Cumret")

#  Extract the weighted returns for each constituent from Q3, and change to wide format to use princomp.
# In addition, I transform the simple returns to log returns and mean-centre them


df_Port_ret_final <- df_Port_ret |> arrange(date) |> 
    
    group_by(date, Sector) |>       # Group by Market Cap to calc each category's contr to wieghted portf return
    
    mutate(ALSI_wght_sector = coalesce(J400, 0)) |> # Make NA's 0 to use PA later
    
    mutate(SWIX_wght_sector = coalesce(J200, 0)) |>
    
    mutate(ALSI_wret = coalesce(ALSI_wret, 0)) |> 
    
    mutate(SWIX_wret = coalesce(SWIX_wret, 0)) |>
    
    mutate(ALSI_ret_sector = sum(ALSI_wret, na.rm = T)) |>  # The weight-contribution of each sector on each day
    
    mutate(SWIX_ret_sector = sum(SWIX_wret, na.rm = T)) |>

    mutate(ALSI_wght_sector = sum(J400, na.rm = T)) |>  # The weighted return contribution of each sector on each day
    
    mutate(SWIX_wght_sector = sum(J200, na.rm = T)) |>
    
    ungroup()

ALSI_wght_sector <-  df_Port_ret_final |> select(date, Sector ,ALSI_wght_sector) |> group_by(Sector) |> unique() |> 
    tbl_xts(cols_to_xts = ALSI_wght_sector, spread_by = Sector)

SWIX_wght_sector <- df_Port_ret_final |> select(date, Sector ,SWIX_wght_sector) |> group_by(Sector) |> unique() |> 
    tbl_xts(cols_to_xts = SWIX_wght_sector, spread_by = Sector)

ALSI_ret_sector <- df_Port_ret_final |> select(date, Sector ,ALSI_ret_sector) |> group_by(Sector) |> unique() |> 
    tbl_xts(cols_to_xts = ALSI_ret_sector, spread_by = Sector)

SWIX_ret_sector <- df_Port_ret_final |> select(date, Sector ,SWIX_ret_sector) |> group_by(Sector) |> unique() |> 
    tbl_xts(cols_to_xts = SWIX_ret_sector, spread_by = Sector)



 ALSI_RetPort_sector <- 
      rmsfuns::Safe_Return.portfolio(ALSI_ret_sector, 
                                     
                       weights = ALSI_wght_sector, lag_weights = TRUE,
                       
                       verbose = TRUE, contribution = TRUE, 
                       
                       value = 1000, geometric = TRUE) 

 SWIX_RetPort_sector <- 
      rmsfuns::Safe_Return.portfolio(SWIX_ret_sector, 
                                     
                       weights = SWIX_wght_sector, lag_weights = TRUE,
                       
                       verbose = TRUE, contribution = TRUE, 
                       
                       value = 1000, geometric = TRUE)
    

 ALSI_RetPort_sector$BOP.Weight  %>% .[endpoints(.,'months')] %>% chart.StackedBar()
 
  SWIX_RetPort_sector$BOP.Weight  %>% .[endpoints(.,'months')] %>% chart.StackedBar()

  ALSI_RetPort_sector$contribution |> chart.CumReturns(legend.loc = "bottom")
  
  SWIX_RetPort_sector$contribution |> chart.CumReturns(legend.loc = "bottom")
 
  
  # I firt pull the effective rebalance dates

Rebalance_Days <-RebDays |> filter(Date_Type %in% c("Effective Date")) |> pull(date)
    
# And now for both Indexes I create a capped weights tbl for rebalancing purposes

rebalance_col_ALSI <- T40_a |> 
    
    filter(date %in% Rebalance_Days) |> 
    
    select(date, Tickers, J200) |> 
    
    rename(weight = J200) |> 
    
    mutate(RebalanceTime = format(date, "%Y_%b")) |> 
    
    mutate(weight= coalesce(weight, 0))
    
 rebalance_col_SWIX <- T40_a |> 
    
    filter(date %in% Rebalance_Days) |> 
    
    select(date, Tickers, J400) |> 
     
     rename(weight = J400) |> 
     
     mutate(RebalanceTime = format(date, "%Y_%b")) |> 
     
      mutate(weight= coalesce(weight, 0))
 
 Proportional_Cap_Foo <- function(df_Cons, W_Cap = 0.08){
  
  # Let's require a specific form from the user... Alerting when it does not adhere this form
  if( !"weight" %in% names(df_Cons)) stop("... for Calc capping to work, provide weight column called 'weight'")
  
  if( !"date" %in% names(df_Cons)) stop("... for Calc capping to work, provide date column called 'date'")
  
  if( !"Tickers" %in% names(df_Cons)) stop("... for Calc capping to work, provide id column called 'Tickers'")

  # First identify the cap breachers...
  Breachers <- 
    df_Cons %>% filter(weight > W_Cap) %>% pull(Tickers)
  
  # Now keep track of breachers, and add to it to ensure they remain at 10%:
  if(length(Breachers) > 0) {
    
    while( df_Cons %>% filter(weight > W_Cap) %>% nrow() > 0 ) {
      
      
      df_Cons <-
        
        bind_rows(
          
          df_Cons %>% filter(Tickers %in% Breachers) %>% mutate(weight = W_Cap),
          
          df_Cons %>% filter(!Tickers %in% Breachers) %>% 
            mutate(weight = (weight / sum(weight, na.rm=T)) * (1-length(Breachers)*W_Cap) )
          
        )
      
      Breachers <- c(Breachers, df_Cons %>% filter(weight > W_Cap) %>% pull(Tickers))
      
    }

    if( sum(df_Cons$weight, na.rm=T) > 1.001 | sum(df_Cons$weight, na.rm=T) < 0.999 | max(df_Cons$weight, na.rm = T) > W_Cap) {
      
      stop( glue::glue("For the Generic weight trimming function used: the weight trimming causes non unit 
      summation of weights for date: {unique(df_Cons$date)}...\n
      The restriction could be too low or some dates have extreme concentrations...") )
      
    }
    
  } else {
    
  }
  
  df_Cons
  
  }
  

# Now, to map this across all the dates, I purrr::map_df 
Capped_ALSI_10 <- 
    
    rebalance_col_ALSI |> 

    group_split(RebalanceTime) |> 
    
    map_df(~Proportional_Cap_Foo(., W_Cap = 0.1) ) |>  select(-RebalanceTime)
  
# Now I do the same for a 6% cap:

Capped_ALSI_6 <- 
    
    rebalance_col_ALSI |> 

    group_split(RebalanceTime) |> 
    
    map_df(~Proportional_Cap_Foo(., W_Cap = 0.06) ) |>  select(-RebalanceTime)

Capped_SWIX_10 <- 
    
    rebalance_col_ALSI |> 

    group_split(RebalanceTime) |> 
    
    map_df(~Proportional_Cap_Foo(., W_Cap = 0.1) ) |>  select(-RebalanceTime)
  
Capped_SWIX_6 <- 
    
    rebalance_col_ALSI |> 

    group_split(RebalanceTime) |> 
    
    map_df(~Proportional_Cap_Foo(., W_Cap = 0.06) ) |>  select(-RebalanceTime)

# # Testing if the max weight is correct for all 4 tbl above

Capped_ALSI_10 %>% pull(weight) %>% max(.) 
Capped_ALSI_6 %>% pull(weight) %>% max(.) 
Capped_SWIX_10 %>% pull(weight) %>% max(.) 
Capped_SWIX_6 %>% pull(weight) %>% max(.) # Success!!


####For ALSI capped at 10%#####

wghts_ALSI_10 <- 
  Capped_ALSI_10 %>% 
  tbl_xts(cols_to_xts = weight, spread_by = Tickers)

ret_ALSI_10 <- 
  T40_a %>% 
  
  filter(Tickers %in% unique(Capped_ALSI_10$Tickers) ) %>% 
  
  tbl_xts(cols_to_xts = Return, spread_by = Tickers)

wghts_ALSI_10[is.na(wghts_ALSI_10)] <- 0

ret_ALSI_10[is.na(ret_ALSI_10)] <- 0

ALSI_10_Idx <- 
  rmsfuns::Safe_Return.portfolio(R = ret_ALSI_10, weights = wghts_ALSI_10, lag_weights = T) |> 
  
  # Then I make it a tibble:
  xts_tbl() |>  
  
  rename(ALSI_10_Idx = portfolio.returns)

####For ALSI capped at 6%#####

wghts_ALSI_6 <- 
  Capped_ALSI_6 %>% 
  tbl_xts(cols_to_xts = weight, spread_by = Tickers)

ret_ALSI_6 <- 
  T40_a %>% 
  
  filter(Tickers %in% unique(Capped_ALSI_6$Tickers) ) %>% 
  
  tbl_xts(cols_to_xts = Return, spread_by = Tickers)

wghts_ALSI_6[is.na(wghts_ALSI_6)] <- 0

ret_ALSI_6[is.na(ret_ALSI_6)] <- 0

ALSI_6_Idx <- 
  rmsfuns::Safe_Return.portfolio(R = ret_ALSI_6, weights = wghts_ALSI_6, lag_weights = T) |> 
  
  # Then I make it a tibble:
  xts_tbl() |>  
  
  rename(ALSI_6_Idx = portfolio.returns)

####For SWIX capped at 10%#####

wghts_SWIX_10 <- 
  Capped_SWIX_10 %>% 
  tbl_xts(cols_to_xts = weight, spread_by = Tickers)

ret_SWIX_10 <- 
  T40_a %>% 
  
  filter(Tickers %in% unique(Capped_SWIX_10$Tickers) ) %>% 
  
  tbl_xts(cols_to_xts = Return, spread_by = Tickers)

wghts_SWIX_10[is.na(wghts_SWIX_10)] <- 0

ret_SWIX_10[is.na(ret_SWIX_10)] <- 0

SWIX_10_Idx <- 
  rmsfuns::Safe_Return.portfolio(R = ret_SWIX_10, weights = wghts_SWIX_10, lag_weights = T) |> 
  
  # Then I make it a tibble:
  xts_tbl() |>  
  
  rename(SWIX_10_Idx = portfolio.returns)



####For SWIX capped at 6%#####

wghts_SWIX_6 <- 
  Capped_SWIX_6 %>% 
  tbl_xts(cols_to_xts = weight, spread_by = Tickers)

ret_SWIX_6 <- 
  T40_a %>% 
  
  filter(Tickers %in% unique(Capped_SWIX_6$Tickers) ) %>% 
  
  tbl_xts(cols_to_xts = Return, spread_by = Tickers)

wghts_SWIX_6[is.na(wghts_SWIX_6)] <- 0

ret_SWIX_6[is.na(ret_SWIX_6)] <- 0

SWIX_6_Idx <- 
  rmsfuns::Safe_Return.portfolio(R = ret_SWIX_6, weights = wghts_SWIX_6, lag_weights = T) |> 
  
  # Then I make it a tibble:
  xts_tbl() |>  
  
  rename(SWIX_6_Idx = portfolio.returns)

Capped_df_final <- ALSI_6_Idx |> inner_join(ALSI_10_Idx, by ="date") |> 
    inner_join(SWIX_6_Idx, by ="date") |> 
    inner_join(SWIX_10_Idx, by ="date") |>
    
    arrange(date) |> 
    mutate(across(.cols = -date, .fns = ~cumprod(1+.))) |> # cumulative returns
    mutate(across(.cols = -date, .fns = ~./first(.))) |>   # Start at 1
    inner_join(Cum_ret |> pivot_wider(names_from= "Index", values_from= "Cumret"), by = "date") |> # Add the uncapped cumret 
    
    rename("ALSI Capped 6%" = ALSI_6_Idx, "ALSI Capped 10%" = ALSI_10_Idx,"SWIX Capped 6%" =  SWIX_6_Idx, "SWIX Capped 10%" =  SWIX_10_Idx, "Uncapped SWIX" = SWIX, "Uncapped ALSI" = ALSI) |> # rename for clarity
    
    pivot_longer(cols = -date, names_to = "Description", values_to = "Values")



```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

# ALSI and SWIX (uncapped) Weighted Portfolio Returns

Figure \ref{Figure1} plots the weighted (uncapped) cumulative returns series for the ALSI and SWIX indexes. The cumulative weighted returns for the ALSI and SWIX indexes are strikingly similar, however, since the onset of COVID-19, the ALSI has achieved higher returns. 

```{r Indexes_Cum_ret_plot,  warning =  FALSE, fig.align = 'center', fig.cap = "Cumulative Returns of ALSI and SWIX Indexes Per Sector. \\label{Figure1}", fig.ext = 'png', fig.height = 4, fig.width = 6}

Indexes_Cum_ret_plot <-    Cum_ret |> 
       
       ggplot() + 
  
  geom_line(aes(date, Cumret , color = Index), size = 0.6, alpha = 0.7) +
  
   fmxdat::theme_fmx(title.size = fmxdat::ggpts(30), 
                    subtitle.size = fmxdat::ggpts(0),
                    caption.size = fmxdat::ggpts(25),
                    CustomCaption = T) + 
    
  fmxdat::fmx_cols() + 
  
  labs(x = "", y = "%", caption = "Note:\nCalculation own",
       title = "Cumulative Returns of ALSI and SWIX Indexes",
       subtitle = "")

# Finplot for finishing touches:

fmxdat::finplot(Indexes_Cum_ret_plot, x.vert = T, x.date.type = "%Y", x.date.dist = "1 year", darkcol = T)


```


# Weighted Return Contribition per Sector 

In order to shed some light on SWIX's relatively weaker performance since the onset of COVID, I analyse the dynamic weighted contribution of of each sector to the indexes. Figures \ref{Figure2} and \ref{Figure3} shows the dynamic weight contribution to the ALSI and SWIX portfolios, respectively. 

In considering the ALSI in Figure \ref{Figure2}, a capping of 10% has virtually the same cumulative returns as when uncapped, with significantly lower returns when capped at 6%. This is likely due to this 6% capping most of the relatively higher returns generated from the Resources sector. On the other hand, from the SWIX in Figure \ref{Figure3}, the 10% cap would have improved its return since the onset of COVID, most likely due to a reduction in weighted contribution from the weaker performing Industrial and Financial sectors. 

```{r ALSI weights plot,  warning =  FALSE, fig.align = 'center', fig.cap = "Dynamic Weight Contribution to ALSI Portfolio Per Sector. \\label{Figure2}", fig.ext = 'png', fig.height = 3.5, fig.width = 6}

ALSI_RetPort_sector$BOP.Weight  %>% .[endpoints(.,'months')] %>% chart.StackedBar()


```

```{r SWIX weights plot,  warning =  FALSE, fig.align = 'center', fig.cap = "Dynamic Weight Contribution to SWIX Portfolio. \\label{Figure3}", fig.ext = 'png', fig.height = 3.5, fig.width = 6}

SWIX_RetPort_sector$BOP.Weight  %>% .[endpoints(.,'months')] %>% chart.StackedBar()



```

Figures \ref{Figure4} and \ref{Figure5} confirms the analyses above.

```{r ALSI contr plot,  warning =  FALSE, fig.align = 'center', fig.cap = "Dynamic Weighted Return Contribution to SWIX Portfolio Per Sector. \\label{Figure4}", fig.ext = 'png', fig.height = 3.5, fig.width = 6}

ALSI_RetPort_sector$contribution |> chart.CumReturns(legend.loc = "bottom")
  


```

```{r SWIX contr plot,  warning =  FALSE, fig.align = 'center', fig.cap = "Dynamic Weighted Return Contribution to SWIX Portfolio Per Sector. \\label{Figure5}", fig.ext = 'png', fig.height = 3.5, fig.width = 6}

  SWIX_RetPort_sector$contribution |> chart.CumReturns(legend.loc = "bottom")



```


# Counterfactual 6% and 10% Capped ALSI and SWIX Returns

Figures \ref{Figure6} and \ref{Figure7} shows the counterfactual impact that 6% and 10% capping levels would have had on both the SWIX and ALSI, respectively. In investigating these figures, it is apparent that a 6% cap on the ALSI would have significantly reduced its performance in the past few years due to slicing the weights on the higher returning Resources sector. On the other hand, the 10% cap on SWIX would have improved its return since the onset of COVID, likely due to a reduction in weighted contribution from the weaker-performing Industrial and Financial sectors.

```{r ALSI capping plot,  warning =  FALSE, fig.align = 'center', fig.cap = "Cumulative Returns of ALSI Capped at 6 and 10 Percent. \\label{Figure6}", fig.ext = 'png', fig.height = 4, fig.width = 6}

capping_plot_ALSI <- 

Capped_df_final |> filter(Description %in% c("ALSI Capped 6%", "ALSI Capped 10%", "Uncapped ALSI"))  |> 

    ggplot() + 
  
  geom_line(aes(date, Values , color = Description), size = 0.8, alpha = 0.7) +
  
   fmxdat::theme_fmx(title.size = fmxdat::ggpts(30), 
                    subtitle.size = fmxdat::ggpts(0),
                    caption.size = fmxdat::ggpts(25),
                    CustomCaption = T) + 
    
  fmxdat::fmx_cols() + 
  
  labs(x = "", y = "%", caption = "Note:\nCalculation own",
       title = "Cumulative Returns of ALSI Capped at 6% and 10%",
       subtitle = "")


# Finplot for finishing touches:

fmxdat::finplot(capping_plot_ALSI, x.vert = T, x.date.type = "%Y", x.date.dist = "1 year", darkcol = T)


```



```{r SWIX capping plot,  warning =  FALSE, fig.align = 'center', fig.cap = "Cumulative Returns of SWIX Capped at 6 and 10 Percent. \\label{Figure7}", fig.ext = 'png', fig.height = 4, fig.width = 6}

capping_plot_SWIX <- 

Capped_df_final |> filter(Description %in% c("SWIX Capped 6%", "SWIX Capped 10%", "Uncapped SWIX"))  |> 

    ggplot() + 
  
  geom_line(aes(date, Values , color = Description), size = 0.8, alpha = 0.7) +
  
   fmxdat::theme_fmx(title.size = fmxdat::ggpts(30), 
                    subtitle.size = fmxdat::ggpts(0),
                    caption.size = fmxdat::ggpts(25),
                    CustomCaption = T) + 
    
  fmxdat::fmx_cols() + 
  
  labs(x = "", y = "%", caption = "Note:\nCalculation own",
       title = "Cumulative Returns of SWIX Capped at 6% and 10%",
       subtitle = "")

# Finplot for finishing touches:


fmxdat::finplot(capping_plot_SWIX, x.vert = T, x.date.type = "%Y", x.date.dist = "1 year", darkcol = T)


```




<!-- Make title of bibliography here: -->
<!-- \newpage -->

\newpage

# References {-}

<div id="refs"></div>
