---
# IMPORTANT: Change settings here, but DO NOT change the spacing.
# Remove comments and add values where applicable.
# The descriptions below should be self-explanatory

title: "Financial Econometrics 871 Practical Exam 2022: Question 4"
subtitle: "Question 4"

documentclass: "elsarticle"

# --------- Thesis title (Optional - set to FALSE by default).
# You can move the details below around as you please.
Thesis_FP: FALSE
# Entry1: "An unbelievable study with a title spanning multiple lines."
# Entry2: "\\textbf{Nico Katzke}" # textbf for bold
# Entry3: "A thesis submitted toward the degree of Doctor of Philosophy"
# Uni_Logo: Tex/Logo.png # Place a logo in the indicated location (from your root, e.g. defaults to ~/Tex/Logo.png) and uncomment this line. Leave uncommented for no image
# Logo_width: 0.3 # If using a logo - use this to set width (size) of image
# Entry4: "Under the supervision of: \\vfill Prof. Joe Smith and Dr. Frank Smith"
# Entry5: "Stellenbosch University"
# Entry6: April 2020
# Entry7:
# Entry8:

# --------- Front Page
# Comment: ----- Follow this pattern for up to 5 authors
AddTitle: TRUE # Use FALSE when submitting to peer reviewed platform. This will remove author names.
Author1: "Tian Cater"  # First Author - note the thanks message displayed as an italic footnote of first page.
Ref1: "University of Stellenbosch, Western Cape, South Africa^[2022-11-27]" # First Author's Affiliation
Email1: "19025831\\@sun.ac.za" # First Author's Email address

#Author2: "John Smith"
#Ref2: "Some other Institution, Cape Town, South Africa"
#Email2: "John\\@gmail.com"
#CommonAffiliation_12: TRUE # If Author 1 and 2 have a common affiliation. Works with _13, _23, etc.

#Author3: "John Doe"
#Email3: "Joe\\@gmail.com"

#CorrespAuthor_1: TRUE  # If corresponding author is author 3, e.g., use CorrespAuthor_3: TRUE

# Comment out below to remove both. JEL Codes only given if keywords also given.
#keywords: "Multivariate GARCH \\sep Kalman Filter \\sep Copula" # Use \\sep to separate
#JELCodes: "L250 \\sep L100"

# ----- Manage headers and footers:
#BottomLFooter: $Title$
#BottomCFooter:
#TopLHeader: \leftmark # Adds section name at topleft. Remove comment to add it.
BottomRFooter: "\\footnotesize Page \\thepage" # Add a '#' before this line to remove footer.
addtoprule: TRUE
addfootrule: TRUE               # Use if footers added. Add '#' to remove line.

# --------- page margins:
margin: 2.3 # Sides
bottom: 2 # bottom
top: 2.5 # Top
HardSet_layout: TRUE # Hard-set the spacing of words in your document. This will stop LaTeX squashing text to fit on pages, e.g.
# This is done by hard-setting the spacing dimensions. Set to FALSE if you want LaTeX to optimize this for your paper.

# --------- Line numbers
linenumbers: FALSE # Used when submitting to journal

# ---------- References settings:
# You can download cls format here: https://www.zotero.org/ - simply search for your institution. You can also edit and save cls formats here: https://editor.citationstyles.org/about/
# Hit download, store it in Tex/ folder, and change reference below - easy.
bibliography: Tex/ref.bib       # Do not edit: Keep this naming convention and location.
csl: Tex/harvard-stellenbosch-university.csl # referencing format used.
# By default, the bibliography only displays the cited references. If you want to change this, you can comment out one of the following:
#nocite: '@*' # Add all items in bibliography, whether cited or not
# nocite: |  # add specific references that aren't cited
#  @grinold2000
#  @Someoneelse2010

# ---------- General:
RemovePreprintSubmittedTo: TRUE  # Removes the 'preprint submitted to...' at bottom of titlepage
Journal: "Journal of Finance"   # Journal that the paper will be submitting to, if RemovePreprintSubmittedTo is set to TRUE.
toc: FALSE                       # Add a table of contents
numbersections: TRUE             # Should sections (and thus figures and tables) be numbered?
fontsize: 11pt                  # Set fontsize
linestretch: 1.2                # Set distance between lines.
link-citations: TRUE            # This creates dynamic links to the papers in reference list.

### Adding additional latex packages:
# header-includes:
#    - \usepackage{colortbl} # Add additional packages here.

output:
  pdf_document:
    keep_tex: TRUE
    template: Tex/TexDefault.txt
    fig_width: 3.5 # Adjust default figure sizes. This can also be done in the chunks of the text.
    fig_height: 3.5
abstract: |
  In this question, I use the Top 40 Index data from question 3 to calculate the concentration of returns among the ALSI constituents (J200) by considering it from a Principal Component Analysis (PCA) perspective. I plot the Scree plot (percentage of explained variances) and the Cos2 plot (quality of representation) for the principal components that explain the most volatility (quality of representation). The findings suggest that NPN, BHP, and AGL explain a significant portion of the ALSI Top 40 index variation.
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

# Lets load in example data, and see how this can be stored and later called from your 'data' folder.
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)

pacman::p_load("RiskPortfolios", "FactoMineR", "factoextra", "broom")
pacman::p_load("tidyverse","fmxdat", "dplyr", "rmsfuns", "PerformanceAnalytics", "tbl2xts", "xts", "rportfolios", "Texevier", "kableExtra", "ggplot2", "extrafont", "devtools")

T40 <- read_rds("C:/Users/tianc/Rproj/FinMetrics871_Exam/19025831/data/T40.rds") # There are 92 stocks in this tbl

RebDays <- read_rds("C:/Users/tianc/Rproj/FinMetrics871_Exam/19025831/data/Rebalance_days.rds")

Capped_SWIX <- read_rds("C:/Users/tianc/Rproj/FinMetrics871_Exam/19025831/data/Capped_SWIX.rds") # This is the Monthly Capped and Weighted Portf Returns for SWIX Index (J433)

# I first shrink the dataframe to include only what in needed

T40_a <- T40 |> select(-Short.Name) |> 
    
    mutate(Tickers = gsub(" SJ Equity", "", Tickers))  # Remove clutter in Tickers names


# I generate a tbl calculating both Indexes weighted returns by hand

df_Port_ret <- T40_a |> 
    
    mutate(J400 = coalesce(J400, 0)) |> 
    
    mutate(J400 = coalesce(J400, 0)) |> 
    
    mutate(ALSI_wret = Return*J200) |> 
    
    mutate(SWIX_wret = Return*J400) |> 
    
    arrange(date) |> 
    
    group_by(date) |> 
    
    mutate(ALSI_pret = sum(ALSI_wret)) |> 
    
    mutate(SWIX_pret = sum(SWIX_wret)) 

# Lets calculate the weighted portfolio daily return for ALSI and SWIX using Safe_Returns to verify my by hand calculation

Wghts_ALSI_xts <- T40_a |> select(date, Tickers , J200) |> tbl_xts(cols_to_xts = J200, spread_by = Tickers)

Wghts_SWIX_xts <- T40_a |> select(date, Tickers , J400) |> tbl_xts(cols_to_xts = J400, spread_by = Tickers)

Returns_xts <- T40_a |> select(date, Tickers , Return) |> tbl_xts(cols_to_xts = Return, spread_by = Tickers)

# Set NA's to null to use PA's Safe_returns.Portfolio command

Wghts_ALSI_xts[is.na(Wghts_ALSI_xts)] <- 0
Wghts_SWIX_xts[is.na(Wghts_SWIX_xts)] <- 0
Returns_xts[is.na(Returns_xts)] <- 0

# Now I calculate the weighed (uncapped) portfolio returns

Port_Ret_ALSI <- rmsfuns::Safe_Return.portfolio(R = Returns_xts, weights = Wghts_ALSI_xts, lag_weights = T) |> 
    
                 xts_tbl() |> rename(ALSI_Ret = portfolio.returns)

Port_Ret_SWIX <- rmsfuns::Safe_Return.portfolio(R = Returns_xts, weights = Wghts_SWIX_xts, lag_weights = T) |> 
    
                 xts_tbl() |> rename(SWIX_Ret = portfolio.returns)

# Now I combine the above two weighted portfolio returns

Merged_Port_Ret <- inner_join(Port_Ret_ALSI, Port_Ret_SWIX, by= "date")

# I verify that my by hand calc and the Safe_return calc is the same:
# df_Port_ret |> select(date, ALSI_pret, SWIX_pret) |> group_by(date, ALSI_pret, SWIX_pret ) |> summarise()
# Happy ---> They are the same

# Now I proceed to calculate the Portfolios' cumulative return and plot it

Cum_ret <- Merged_Port_Ret |> arrange(date) |> 
    
    mutate(across(.cols = -date, .fns = ~cumprod(1 + .))) |> 
    
    mutate(across(.cols = -date, .fns = ~./first(.))) |> # Start at 1
    
    rename(ALSI = ALSI_Ret, SWIX= SWIX_Ret) |> 
    
    pivot_longer(cols=-date, names_to = "Index", values_to = "Cumret")

#  Extract the weighted returns for each constituent from Q3, and change to wide format to use princomp.
# In addition, I transform the simple returns to log returns and mean-centre them


PCA_data <- df_Port_ret |> select(date, Tickers, ALSI_wret) |>
    
    mutate(log_ret = exp(ALSI_wret)-1) |>            # convert to log returns
    
    arrange(date) |> group_by(Tickers) |> 
    
    mutate(log_ret = log_ret - mean(log_ret)) |>   # Mean-centering
    
    ungroup() |> select(-ALSI_wret) |> 
    
    pivot_wider(names_from = "Tickers", values_from = "log_ret")

# Now I source the following function from the tut:

impute_missing_returns <- function(return_mat, impute_returns_method = "NONE", Seed = 1234){
  # Make sure we have a date column called date:
  if( !"date" %in% colnames(return_mat) ) stop("No 'date' column provided in return_mat. Try again please.")

  # Note my use of 'any' below...
  # Also note that I 'return' return_mat - which stops the function and returns return_mat. 
  if( impute_returns_method %in% c("NONE", "None", "none") ) {
    if( any(is.na(return_mat)) ) warning("There are missing values in the return matrix.. Consider maybe using impute_returns_method = 'Drawn_Distribution_Own' / 'Drawn_Distribution_Collective'")
    return(return_mat)
  }

  
  if( impute_returns_method  == "Average") {

    return_mat <-
      return_mat %>% gather(Stocks, Returns, -date) %>%
      group_by(date) %>%
      mutate(Avg = mean(Returns, na.rm=T)) %>%
      mutate(Avg = coalesce(Avg, 0)) %>% # date with no returns - set avg to zero
      ungroup() %>%
      mutate(Returns = coalesce(Returns, Avg)) %>% select(-Avg) %>% spread(Stocks, Returns)

    # That is just so much easier when tidy right? See how I gathered and spread again to give back a wide df?
    
  } else

    if( impute_returns_method  == "Drawn_Distribution_Own") {

      set.seed(Seed)
      N <- nrow(return_mat)
      return_mat <-

        left_join(return_mat %>% gather(Stocks, Returns, -date),
                  return_mat %>% gather(Stocks, Returns, -date) %>% group_by(Stocks) %>%
                    do(Dens = density(.$Returns, na.rm=T)) %>%
                    ungroup() %>% group_by(Stocks) %>% # done to avoid warning.
                    do(Random_Draws = sample(.$Dens[[1]]$x, N, replace = TRUE, prob=.$Dens[[1]]$y)),
                  by = "Stocks"
        ) %>%  group_by(Stocks) %>% mutate(Row = row_number()) %>% mutate(Returns = coalesce(Returns, Random_Draws[[1]][Row])) %>%
        select(-Random_Draws, -Row) %>% ungroup() %>% spread(Stocks, Returns)

    } else

      if( impute_returns_method  == "Drawn_Distribution_Collective") {

        set.seed(Seed)
        NAll <- nrow(return_mat %>% gather(Stocks, Returns, -date))

        return_mat <-
          bind_cols(
          return_mat %>% gather(Stocks, Returns, -date),
          return_mat %>% gather(Stocks, Returns, -date) %>%
            do(Dens = density(.$Returns, na.rm=T)) %>%
            do(Random_Draws = sample(.$Dens[[1]]$x, NAll, replace = TRUE, prob=.$Dens[[1]]$y)) %>% unnest(Random_Draws)
          ) %>%
          mutate(Returns = coalesce(Returns, Random_Draws)) %>% select(-Random_Draws) %>% spread(Stocks, Returns)

      } else

        if( impute_returns_method  == "Zero") {
        warning("This is probably not the best idea but who am I to judge....")
          return_mat[is.na(return_mat)] <- 0

        } else
          stop("Please provide a valid impute_returns_method method. Options include:\n'Average', 'Drawn_Distribution_Own', 'Drawn_Distribution_Collective' and 'Zero'.")
}


options(scipen=999) # To remove scientific notation

return_matrix <- 
  impute_missing_returns(PCA_data, impute_returns_method = "Drawn_Distribution_Collective", Seed = as.numeric(format( Sys.time(), "%Y%d%H%M")))

# Remove the date column
return_matrix_Nodate <- data.matrix(return_matrix[, -1])

# Simple Sample covariance and mean:

Sigma <- RiskPortfolios::covEstimation(return_matrix_Nodate)
Mu <- RiskPortfolios::meanEstimation(return_matrix_Nodate)

    
# Conduct PCA:
    
pca <- prcomp(return_matrix_Nodate)   
    


```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

# Scree Plot (percentage of explained variances)

Figure \ref{Figure1} indicates that a single component explains nearly 20% of the variation in the ALSI index. It does not give insight into what this component or factor might be, but it tells us how it is calculated linearly. In addition, excluding the large portion explained by the first two PCs, the remaining seven comprise roughly the same amount of variation in the ALSI.

```{r scree plot,  warning =  FALSE, fig.align = 'center', fig.cap = "Scree Plot of Principal Components of ALSI Top 40. \\label{Figure1}", fig.ext = 'png', fig.height = 4.5, fig.width = 6}

fviz_screeplot(pca, ncp=10)

```


# Cos2 Plot (quality of representation)

Given the significant contribution of the first two components, I generate the cos2 plot below  (Figure \ref{Figure2}) for the first two PCs. Figure \ref{Figure2} shows that NPN, BHP, and AGL have high cos2 values, indicating a good representation of the variable on the first two PCs. 


```{r cos2 plot, scree plot,  warning =  FALSE, fig.align = 'center', fig.cap = "Cos2 Plot of First Two Principal Components of ALSI Top 40. \\label{Figure2}", fig.ext = 'png', fig.height = 4.5, fig.width = 6}

fviz_cos2(pca, choice = "var", axes = 1:2, top = 10)

```




<!-- Make title of bibliography here: -->
<!-- \newpage -->

\newpage

# References {-}

<div id="refs"></div>
